FoRTE baseline

### 2019-09-12 analysis/paper/paper.Rmd
Add very janky intro paragraph about structure

>>>>

<!-- TODO This paragraph is janky as hell. Needs heavy revision. -->
Previous work found that an earlier version of ED had difficulty sustaining multiple plant functional types in long simulations [@fisher_2010_assessing].
One of the primary drivers of successional change in temperate forests is competition for light <!-- TODO REF -- Bazaaz? -->, and differences in plants' strategies for light acquisition and utilization are a key driver of niche differentiation in these ecosystems <!-- TODO REF -->.
To this end, we focused our structural uncertainty analysis on three processes related to competition for light:
Representation of horizontal competition;
representation of canopy radiative transfer (especially of diffuse radiation);
and trait plasticity with light level.
